Content-based recommendations in~e-commerce services

### 2018-02-14 article.tex
intro part

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
	\posttitle{\end{center}} % Article title closing formatting
\title{Article Title} % Article title
\author{%
	\textsc{ŁJohn Smith}\thanks{A thank you or further information} \\[1ex] % Your name
	\normalsize University of California \\ % Your institution
	\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
	%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
	%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
	%\normalsize University of Utah \\ % Second author's institution
	%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
	\begin{abstract}
		\noindent \blindtext % Dummy abstract text - replace \blindtext with your abstract text
	\end{abstract}
}

@@

	%----------------------------------------------------------------------------------------
	%	ARTICLE CONTENTS
	%----------------------------------------------------------------------------------------

@@

@@

	\section{Results}

@@

	\section{Discussion}

@@

	%----------------------------------------------------------------------------------------
	%	REFERENCE LIST
	%----------------------------------------------------------------------------------------

>>>>

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
	\posttitle{\end{center}} % Article title closing formatting
\title{Content-based recommendations in~e-commerce services} % Article title
\author{%
	\textsc{John Smith}\thanks{A thank you or further information} \\[1ex] % Your name
	\normalsize Warsaw University of Technology \\ % Your institution
	\normalsize Faculty of Mathematics and Information Science \\
	\normalsize ul. Koszykowa 75 \\
	\normalsize 00-662 Warsaw, Poland \\
	\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
	%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
	%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
	%\normalsize University of Utah \\ % Second author's institution
	%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
	\begin{abstract}
		The subject of this paper focuses on issues of determining a semantic similarity between text
		documents and recommendations of similar documents. A detailed problem comes from the online
		auction site Allegro, which has a section of articles describing products available on the platform.
		This section offers a recommendation system for similar textual articles based on their
		content. The aim of this paper is to investigate a possibility of improving the existing recommendation
		system using semantic text analysis methods.
		In this paper, I adapt some state-of-the-art methods for determining a similarity between
		text documents to the above problem, I introduce measures to evaluate a performance of these
		methods and analyze possibilities of using them in the real system.
	\end{abstract}
	{\bf Keywords:} recommendations, natural language processing, word embedding, semantics, allegro

}

@@

@@

	Recommendation systems are often part of web services.

	The key issue of recommendations generation is how suggested items are relevant to these which the user is interested in.

	We can divide recommendation systems into two groups: collaborative and  content-based filtering. The first one assumes that user is likely to be interested in items which also users similar to s/he were interested in. In this paper we are focusing on the second group in which recommended items are similar to these that the user liked so far.

	In this paper we strive to check if newly proposed word embeddings methods are able to replace recently used method based on Elasticsearch query.

	Allegro - the biggest marketplace platform in Eastern Europe contains a section presenting text articles concerning products available vie the platform. Currently there is a list of links to articles similar to given one. 
	% cel badania - sprawdzić czy można zastąpić używaną do tej pory metodę opartą o zapytanie elasticsearchowe

@@

	\section{Dataset}

	Given dataset consists of 20000 textual articles concerning different products available via Allegro platform.

	\section{Results and discussion}

	% metody ewaluacji i wyniki

@@

	\section{Conclusion}

@@
